working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
edits

Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a statistically clear correlation for both markers (p<0.05). The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.

>>>>

Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a positive statistically clear correlation for both markers (p<0.05). The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.

add phylogenetic signal of traits...

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
edits

Results of Mantel test between heterospecific pollen effect and
phylogenetic distance gave a statistically clear correlation for both
markers (p\textless{}0.05). The correlations with ITS and RBCL markers
was respectively of 0.29 and 0.25.

>>>>

Results of Mantel test between heterospecific pollen effect and
phylogenetic distance gave a positive statistically clear correlation
for both markers (p\textless{}0.05). The correlations with ITS and RBCL
markers was respectively of 0.29 and 0.25.

add phylogenetic signal of traits\ldots{}
